Developing data load and processing

### 2020-10-16 dev/raw_data_preprocessing.Rmd
Special lab data processing - first working version
Succesful read of special format data

```{r}
devtools::load_all()
library(tidyverse)
```

TODO: code adverse events, code discontinued_medication_reason
TODO: check last day, add outcome to breathing data, possibly

@@

  hospital_data[[i]] <- read_raw_data(file, hospital_id, lang, file_version)
}

@@

```{r}
complete_data <- join_hospital_data(hospital_data)
# TODO check:last day vs. breathing data
# MAx. day vs. read columns
differing_units <- complete_data$marker_data %>% group_by(marker) %>% filter(length(unique(unit)) > 1) %>% 
  group_by(marker, unit) %>% summarise(count = n(), .groups = "drop")

@@

```{r}
for(conversion in unit_conversions) {
  for(marker_to_check in conversion$markers) {
    cat(" ==== ", marker_to_check, "=====\n")
    complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
      pull(value) %>% unique() %>% print()
    print(
      complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
        ggplot(aes(x = value)) + geom_histogram() + facet_wrap(marker ~ unit, scales = "free")
    )
  }
}
```
```{r}
complete_data$marker_data %>% filter(marker == "amoxiclav", value == 0)
```

```{r}
complete_data$marker_data %>% filter(marker == "CRP", unit == "mg/l") %>% pull(hospital_id) %>%   unique()

@@

```{r}
patients_to_merge <- readxl::read_excel(mapping_file, sheet = "PatientsToMerge")
hospitals_to_merge <- readxl::read_excel(mapping_file, sheet = "HospitalsToMerge")
```

```{r}
for(i in 1:(length(hospital_data) - 1)) {
  for(j in (i + 1):length(hospital_data)) {
    #cat(i,",", j,"\n")

```{r}
complete_data <- merge_patients(complete_data, patients_to_merge)

complete_data$patient_data %>% filter(hospital_id == "Oriik", patient_id == 3)
```

>>>>

```{r setup}
devtools::load_all()
library(tidyverse)
```

TODO: check last day

@@

  hospital_data[[hospital_id]] <- read_raw_data(file, hospital_id, lang, file_version)
}

@@

```{r}
complete_data <- join_hospital_data(hospital_data)
# TODO check:last day vs. breathing data
# MAx. day vs. read columns
differing_units <- complete_data$marker_data %>% group_by(marker) %>% filter(length(unique(unit)) > 1) %>% 
  group_by(marker, unit) %>% summarise(count = n(), hospitals = paste0(unique(hospital_id), collapse = ","), .groups = "drop")

@@

```{r}
for(conversion in unit_conversions) {
  for(marker_to_check in conversion$markers) {
    cat(" ==== ", marker_to_check, "=====\n")
    complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
      pull(value) %>% unique() %>% print()
    print(
      complete_data$marker_data %>% filter(marker == marker_to_check, !is.na(value)) %>% 
        ggplot(aes(x = value)) + geom_histogram() + facet_wrap(marker ~ unit, scales = "free")
    )
  }
}
```

```{r}
patients_to_merge <- readxl::read_excel(mapping_file, sheet = "PatientsToMerge", 
                                        col_types = c("text", "text", "text", "text", "text", "numeric", "text"))
hospitals_to_merge <- readxl::read_excel(mapping_file, sheet = "HospitalsToMerge")
```

```{r}
for(i in 1:(length(hospital_data) - 1)) {
  if(names(hospital_data)[i] %in% c("cTdij", "iVMlA","bGzOO", "tMdnA", "nDINR", "vQNDS")) {
    next # Checked manually during date entry
  }
  for(j in (i + 1):length(hospital_data)) {
    #cat(i,",", j,"\n")
    if(names(hospital_data)[j] %in% c("cTdij", "iVMlA","bGzOO", "tMdnA", "nDINR","vQNDS")) {
      next # Checked manually during date entry
    }

```{r}
typeof(patients_to_merge$patient_id1)
complete_data_merged <- merge_patients(complete_data, patients_to_merge)

complete_data$patient_data %>% filter(hospital_id == "Oriik", patient_id == 3)
complete_data_merged$breathing_data %>% filter(hospital_id == "cTdij")
complete_data_merged$patient_data %>% filter(hospital_id == "cTdij")
complete_data$patient_data %>% filter(hospital_id == "cTdij")

@@
